BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-09 background.tex
Minor changes to Background

\begin{figure}[h]
\centering
\includegraphics[scale=0.8]{Figures/Inline.pdf}
\caption{\textit{(a) Ordinary API call execution flow \\
				  (b) API call with inline hooking}}
\end{figure}

@@

On the other hand, a debugger is much easier to detect. In fact, there exist specific Windows APIs whose purpose is to find out whether or not the current process is being debugged. For example, \texttt{IsDebuggerPresent} allows to determine if the calling process is running under a debugger, while \texttt{CheckRemoteDebuggerPresent} checks for the presence of a debugger in a separate process. 
In addition, the \texttt{INT 3} instruction in an API entry point immediately gives away the debugger's presence \cite{HookingDetection}.

@@

\section{Conclusion}

>>>>

\begin{figure}[h]
\centering
\includegraphics[scale=0.8]{Figures/Inline.pdf}
\caption{\textit{(a) Ordinary API call execution flow; (b) API call with inline hooking}}
\end{figure}

@@

On the other hand, a debugger is much easier to detect. In fact, there exist specific Windows APIs whose purpose is to find out whether or not the current process is being debugged. For example, \texttt{IsDebuggerPresent} allows to determine if the calling process is running under a debugger, while \texttt{CheckRemoteDebuggerPresent} checks for the presence of a debugger in a separate process. 
In addition, the \texttt{INT 3} instruction in an API entry point immediately gives away the debugger's presence~\cite{HookingDetection}.

@@

\section{Conclusions}
